\section*{IGO Preparation 2020}

\prob{}
{}{}{
    Let $ABC$ be an arbitrary triangle,$P$ is the intersection point of the altitude from
    $C$ and the tangent line from $A$ to the circumcircle. The bisector of angle $A$
    intersects $BC$ at $D$ . $PD$ intersects $AB$ at $K$, if $H$ is the orthocenter then
    prove : $HK\perp AD$
}

\prob{}
{}{}{
    We have $4$ circles in plane such that any two of them are tangent to each other. we
    connect the tangency point of two circles to the tangency point of two other circles.
    Prove that these three lines are concurrent.
}

\prob{}
{}{}{
    In an acute triangle $ABC$, points $D,E,F$ are the feet of the altitudes from $A,B,C$,
    respectively. A line through $D$ parallel to $EF$ meets $AC$ at $Q$ and $AB$ at $R$.
    Lines $BC$ and $EF$ intersect at $P$. Prove that the circumcircle of triangle $PQR$
    passes through the midpoint of $BC$.
}


\prob{}
{}{}{
    Given $\triangle ABC$ inscribed in $(O)$ an let $I$ and $I_a$ be it's incenter and
    $A$-excenter, respectively.

    Tangent lines to $(O)$ at $C,B$ intersect the angle bisector of $A$ at $M,N$, 
    respectively. Second tangent lines through $M,N$ intersect $(O)$ at $X,Y$.

    Prove that $XYII_a$ is cyclic.
}

\prob{}
{}{}{
    Given triangle $ABC$, $D$ is the foot of the external angle bisector of $A$, $I$ its
    incenter and $I_a$ its $A$-excenter. Perpendicular from $I$ to $DI_a$ intersects the
    circumcircle of triangle in $A'$. Define $B'$ and $C'$ similarly. Prove that $AA',BB'$
    and $CC'$ are concurrent.
}
