\section{Diophantine Equations}
	
	
	\prob{https://artofproblemsolving.com/community/c6h79786p456605}{APMO 1999 P4}{EM}{Determine all pairs $(a,b)$ of integers with the property that the numbers $a^2+4b$ and $b^2+4a$ are both perfect squares.}
	
		\solu{Easy case work assuming positive or negative values for $ a, b $.}
		
		
	
	\prob{https://artofproblemsolving.com/community/c6t177f6h1437607_infinitely_many_pairs}{All Squares}{E}{Prove that there are infinitely many pairs of positive integers $(x, y)$ satisfying that $x+y, x-y, xy+1$ are all perfect squares.}\label{problem:construction_1}
	
		\solu{Just work it out.}
		
		
	
	\prob{https://artofproblemsolving.com/community/c6h418641p2362006}{ISL 2010 N3}{E}{Find the smallest number $n$ such that there exist polynomials $f_1, f_2, \ldots , f_n$ with rational coefficients satisfying \[x^2+7 = f_1\left(x\right)^2 + f_2\left(x\right)^2 + \ldots + f_n\left(x\right)^2.\]}
		
		\solu{Find the obvious answer, which is very small, so we can probably case work it out. We find the case for $ 3 $ a bit challenging. But we plan to show that $ 7a^2 $ can't be written as a sum of $ 3 $ squares. Which numbers can be written as the sum of $ 3 $ squares? Investigate...}
		
		
	\prob{https://artofproblemsolving.com/community/c6h1113199p5083571}{ISL 2014 N5}{E}{Find all triples $(p, x, y)$ consisting of a prime number $p$ and two positive integers $x$ and $y$ such that $x^{p -1} + y$ and $x + y^ {p -1}$ are both powers of $p$.}
		
		\solu{The old school trick, replacement. Assume $ x<y $ and replace $ y $, and then compare the power of $ p $.}