\section{FE cantonmathguy Seclected Problems}



\begin{enumerate}

    


    \item Determine all functions $f: \mathbb{Q} \to \mathbb{Q}$ satisfying $f(x + y) = f(x) + f(y)$ for all $x, y \in \mathbb{Q}$.

    


    \item Let $a_1, a_2, \ldots$ be a sequence of integers with infinitely many positive and negative terms. Suppose that for every positive integer $n$ the numbers $a_1, a_2, \ldots, a_n$ leave $n$ different remainders upon division by $n$. Prove that every integer occurs exactly once in the sequence $a_1, a_2, \ldots$.

    


    \item Determine all functions $f: \mathbb{R} \to \mathbb{R}$ satisfying \[f(x)f(y) = f(x + y) + xy\]for all real $x$ and $y$.

    


    \item Find all functions $f: \mathbb{Z} \rightarrow \mathbb{Z}$ such that, for all integers $a$, $b$, $c$ that satisfy $a + b + c = 0$, the following equality holds:
    \[f(a)^2 + f(b)^2 + f(c)^2 = 2f(a)f(b) + 2f(b)f(c) + 2f(c)f(a).\]

    


    \item Determine all functions $f: \mathbb{R} \to \mathbb{R}$ satisfying
    \[f(x) + f(y) = f(x + y) \quad \text{and} \quad f(xy) = f(x)f(y)\]for all $x, y \in \mathbb{R}$.

    


    \item Find all functions $f: \mathbb{R} \rightarrow \mathbb{R}$ such that for all $x,y \in \mathbb{R}$, the following equality holds
    \[f(\left\lfloor x\right\rfloor y)=f(x)\left\lfloor f(y)\right\rfloor\]where $\left\lfloor a\right\rfloor$ is the greatest integer not greater than $a$.

    


    \item $ \bigstar $ Let $k$ be a real number. Find all functions $f: \mathbb{R} \to \mathbb{R}$ satisfying
    \[|f(x) - f(y)| \le k(x - y)^2\]for all real $x$ and $y$.

    


    \item Let $f: \mathbb{N} \to \mathbb{N}$ be a function, and suppose that positive integers $k$ and $c$ satisfy
    \[f^k(n) = n + c\]for all $n \in \mathbb{N}$, where $f^k$ denotes $f$ applied $k$ times. Show that $k \mid c$.

    


    \item Find all functions $f: \mathbb{N} \to \mathbb{N}$ satisfying
    \[f(f(f(n))) + f(f(n)) + f(n) = 3n\]for every positive integer $n$.

    


    \item Let $S$ be the set of integers greater than $1$. Find all functions $f: S \to S$ such that
    (i) $f(n) \mid n$ for all $n \in S$,
    (ii) $f(a) \ge f(b)$ for all $a, b \in S$ with $a \mid b$.

    


    \item Let $\mathbb{R}$ be the set of real numbers. Determine all functions $f: \mathbb{R} \to \mathbb{R}$ such that \[f(x^2 - y^2) = x f(x) - y f(y)\]for all pairs of real numbers $x$ and $y$.

    


    \item $ \bigstar $ Let $T$ denote the set of all ordered triples $(p,q,r)$ of nonnegative integers. Find all functions $f: T \to \mathbb{R}$ satisfying
    \[f(p,q,r) = \begin{cases} 0 & \text{if} \; pqr = 0, \\ 1 + \frac{1}{6}(f(p + 1,q - 1,r) + f(p - 1,q + 1,r) & \\ + f(p - 1,q,r + 1) + f(p + 1,q,r - 1) & \\ + f(p,q + 1,r - 1) + f(p,q - 1,r + 1)) & \text{otherwise} \end{cases} \]for all nonnegative integers $p$, $q$, $r$.

    


    \item Determine all strictly increasing functions $f: \mathbb{N} \to \mathbb{N}$ satisfying $nf(f(n)) = f(n)^2$ for all positive integers $n$.

    


    \item Determine all functions $f: \mathbb{Z} \rightarrow \mathbb{Z}$ with the property that
    \[f(x - f(y)) = f(f(x)) - f(y) - 1\]holds for all $x,y \in \mathbb{Z}$.

    


    \item Find all real-valued functions $f$ defined on pairs of real numbers, having the following property: for all real numbers $a, b, c$, the median of $f(a,b), f(b,c), f(c,a)$ equals the median of $a, b, c$.

    


    \item Find all functions $f: \mathbb{N} \rightarrow \mathbb{N}$ such that, for all positive integer $n$, we have $f(f(n)) < f(n + 1)$.

    


    \item Let $f: \mathbb{N} \to \mathbb{N}$ be a function such that, for any $w, x, y, z \in N$,
    \[f(f(f(z))) f(wxf(yf(z))) = z^2 f(xf(y)) f(w).\]Show that $f(n!) \ge n!$ for every positive integer $n$.

    


    \item Find all functions $f: \mathbb{N} \rightarrow \mathbb{N}$ such that $f(n!) = f(n)!$ for all positive integers $n$ and such that $m-n$ divides $f(m) - f(n)$ for all distinct positive integers $m$, $n$.

    


    \item Find all functions $f$ from the reals to the reals such that
    \[(f(a) + f(b))(f(c) + f(d)) = f(ac + bd) + f(ad - bc)\]for all real $a, b, c, d$.

    


    \item Determine all functions $f$ defined on the natural numbers that take values among the natural numbers for which
    \[(f(n))^p \equiv n \pmod{f(p)}\]for all $n \in \mathbb{N}$ and all prime numbers $p$.

    


    \item Let $n \ge 4$ be an integer, and define $[n] = \{1, 2, \ldots, n\}$. Find all functions $W: [n]^2 \to \mathbb{R}$ such that for every partition $[n] = A \cup B \cup C$ into disjoint sets,
    \[\sum_{a \in A} \sum_{b \in B} \sum_{c \in C} W(a,b) W(b,c) = |A| |B| |C|.\]

    


    \item $ \bigstar $ Find all infinite sequences $a_1, a_2, \ldots$ of positive integers satisfying the following properties:
    (a) $a_1 < a_2 < a_3 < \cdots$,
    (b) there are no positive integers $i$, $j$, $k$, not necessarily distinct, such that $a_i + a_j = a_k$,
    (c) there are infinitely many $k$ such that $a_k = 2k - 1$.

    


    \item Show that there exists a bijective function $f:\mathbb N_0\to\mathbb N_0$ such that for all $m,n\in\mathbb{N}_{0}$, $$f(3mn + m + n) = 4f(m)f(n) + f(m) + f(n)$$

    


    \item Determine all functions $f: \mathbb Z \to \mathbb Z$ satisfying $$f(f(m) + n) + f(m) = f(n) + f(3m) + 2014$$ for all integers $m$ and $n$.

    


    \item Let $n \ge 3$ be a given positive integer. We wish to label each side and each diagonal of a regular $n$-gon $P_1 \ldots P_n$ with a positive integer less than or equal to $r$ so that:

\begin{enumerate}

	    


        \item every integer between $1$ and $r$ occurs as a label;
        


        \item in each triangle $P_iP_jP_k$ two of the labels are equal and greater than the third.

\end{enumerate}
    
    Given these conditions:

\begin{enumerate}

        


        \item Determine the largest positive integer $r$ for which this can be done.
        


        \item For that value of $r$, how many such labellings are there?

\end{enumerate}

    


    \item $ \bigstar $ Suppose that $f$ and $g$ are two functions defined on the set of positive integers and taking positive integer values. Suppose also that the equations $f(g(n)) = f(n) + 1$ and $g(f(n)) = g(n) + 1$ hold for all positive integer $n$. Prove that $f(n) = g(n)$ for all positive integer $n$.

    


    \item Find all the functions $f: \mathbb N_0 \to \mathbb N_0$ satisfying the relation

    


    \item Let $\mathbb{R}$ be the set of real numbers. Determine all functions $f: \mathbb{R} \to \mathbb{R}$ that satisfy the equation
    \[f(x + f(x + y)) + f(xy) = x + f(x + y) + yf(x)\]for all real numbers $x$ and $y$.

    


    \item Suppose that $s_1, s_2, s_3, \ldots$ is a strictly increasing sequence of positive integers such that the sub-sequences
    \[s_{s_1}, s_{s_2}, s_{s_3}, \ldots \qquad\text{and}\qquad s_{s_1+1}, s_{s_2+1}, s_{s_3+1}, \ldots\]are both arithmetic progressions. Prove that the sequence $s_1, s_2, s_3, \ldots$ is itself an arithmetic progression.

    


    \item Find all functions $f$ from $\mathbb{N}_0$ to itself such that
    \[f(m + f(n)) = f(f(m)) + f(n)\]for all $m, n \in \mathbb{N}_0$.

    


    \item $ \bigstar $ Consider a function $f: \mathbb{N} \to \mathbb{N}$. For any $m, n \in \mathbb{N}$ we write $f^n(m) = \underbrace{f(f(\ldots f}_{n}(m)\ldots))$. Suppose that $f$ has the following two properties:

\begin{enumerate}

	   


       \item if $m, n \in \mathbb{N}$, then $\frac{f^n(m) - m}{n} \in \mathbb{N}$;
        


        \item The set $\mathbb{N} \setminus \{f(n) \mid n\in \mathbb{N}\}$ is finite.

\end{enumerate}
    
    Prove that the sequence $f(1) - 1, f(2) - 2, f(3) - 3, \ldots$ is periodic.
    
    


    \item Let $\mathbb{N}$ be the set of positive integers. Find all functions $f: \mathbb{N} \to \mathbb{N}$ that satisfy the equation
    \[f^{abc-a}(abc) + f^{abc-b}(abc) + f^{abc-c}(abc) = a + b + c\]for all $a,b,c \ge 2$.

    


    \item Let $2\mathbb{Z} + 1$ denote the set of odd integers. Find all functions $f:\mathbb{Z} \to 2\mathbb{Z} + 1$ satisfying
    \[f(x + f(x) + y) + f(x - f(x) - y) = f(x + y) + f(x - y)\]for every $x, y \in \mathbb{Z}$.

\end{enumerate}